---
title: "R Markdown documents are awesome"
author: "! Your name here !"
date: "30/10/2019"
output:
  pdf_document: default
  html_document: default
---

# Introduction

Welcome to R Markdown! This is your working document. Instructions on what to do with this document can be found on github.com/riinuots/markdown


```{r setup, include=FALSE}
# This chunk can be used to set some defaults for the whole document
knitr::opts_chunk$set(echo = TRUE)
```



# Data and set-up

Loading the packages:

```{r}

library(tidyverse)
library(knitr)
library(gapminder)

```

We are using the gapminder dataset:

```{r}

gapminder = gapminder %>% 
  # round gdpPercap to 0 decimals:
  mutate(gdpPercap = round(gdpPercap)) %>% 
  # divide pop by million, round to 1 decimal:
  mutate(pop_millions = (pop/1e6) %>% round(1))


```

# Table

A random sample of rows in the dataset:
```{r}

gapminder %>% 
  select(-pop) %>% 
  sample_n(10) %>% 
  kable()

```


Number of variables: `r gapminder %>% ncol()`.

Total number of observations: `r gapminder %>% nrow()`.


# Plotting

```{r}
gapminder %>% 
  filter(year == 2007) %>% 
  ggplot(aes(x      = gdpPercap/1000, #divide by 1000 to tidy the x-axis
             y      = lifeExp,
             colour = continent,
             size   = pop_millions)) +
  geom_point(shape = 1) +
  theme_bw()
```




